%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem}  % 提供 \uline，加 normalem 可避免改變 \emph 行為
\usepackage{xcolor}          % 若你想加顏色也可以用這個
\usepackage{fontawesome}    
\usepackage[pdftex, colorlinks=true, urlcolor=MidnightBlue]{hyperref}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
    \item {
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
      \end{tabular*}
    }
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
  \vspace{-5pt}
}


\newcommand{\jobSubheading}[3]{  
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small#2} \\  % 第一行：左側是學校/公司，右側是時間範圍（小字斜體）
    \end{tabular*}
    \\ \small #3  % 第二行：Job Overview，左對齊
  \vspace{-5pt}
}
\newcommand{\jobSubItem}[1]{  
  \item \small #1 \vspace{-4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\softBlueLink}[2]{\href{#1}{\textcolor{cyan}{#2}}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Yihsuan Liao} & Email : \href{mailto:logan.yihsuan.liao@gmail.com}{logan.yihsuan.liao@gmail.com}\\
  \faGithub\ \href{https://github.com/yihsuan1102}{Github} \quad \faLinkedin\ \href{https://www.linkedin.com/in/yi-hsuan-liao-a120a3168/}{Linkedin} & Mobile :  \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Cheng Kung University}{Tainan, Taiwan}
      {M.S., Electrical Engineering}{Sep. 2020 -- July 2024}
    \resumeItemListStart
        \resumeItem{Laboratory}{Database and Software Engineering Laboratory (DBSE)}
        \resumeItem{Advisor}{Prof. Hewijin Christine Jiau}
        \resumeItem{Thesis}{What's Leading for Programming Skills}
    \resumeItemListEnd
      
    \resumeSubheading
      {National University of Tainan}{Tainan, Taiwan}
      {B.S., Computer Science and Information Engineering}{Sep. 2016 -- Jun. 2020}
  \resumeSubHeadingListEnd

%-----------Job experience-----------------
\section{Work Experience }
  \resumeSubHeadingListStart
    \jobSubheading
      {National Cheng Kung University}{Oct. 2020 - Jan. 2024}
      {Overview: Improved student affairs service quality through evaluation and automation of administrative workflows, including startup team data management.}
      \resumeItemListStart
        \jobSubItem{Maintained and updated the web platform based on evolving requirements, modifying web content and styles.}
        \jobSubItem{Designed and executed SQL queries to extract and process survey responses from 2,300+ participants.}
        \jobSubItem{Developed an information management system for startup teams based on an existing relational database.}
        \jobSubItem{Implemented a Python script to automatically send customized emails to targeted users, reducing manual email processing time by 90 \%.}
        \jobSubItem{Created technical documentation to record system requirements and design.}
        \jobSubItem{Technologies used: PHP, Python, ASP, JavaScript, MSSQL, CSS, Apache HTTP Server, GitLab.}
      \resumeItemListEnd


\jobSubheading
        {\href{https://www.nutn.edu.tw/vhc/}{National Tainan University}}{Mar. 2020}
      {Overview: A website that presents information about the staff and services of the Visual Impairment Education and Rehabilitation Center.}
      \resumeItemListStart
        \jobSubItem{Conducted requirement analysis via client meetings to clarify content, accessibility, and structure needs.}
        \jobSubItem{Adapted legacy web content into an accessible interface conforming to established accessibility guidelines.}
        \jobSubItem{Utilized Git for version control to manage source code.}
        \jobSubItem{Technologies used: HTML, CSS, Bootstrap, GitLab.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  

%-----------EXPERIENCE-----------------
\section{Project Experience}
  \resumeSubHeadingListStart

    \jobSubheading
       {Full-Stack Software Development}{Sept. 2020 - Jan. 2021}
      {Overview: A web application to help college students enhance their programming skills in Java and C.}
      \resumeItemListStart
        \jobSubItem{Coordinated with an 11-person team using the Agile process.}
        \jobSubItem{Engaged in all stages of the software development lifecycle, including requirements gathering, system design, implementation, testing, and maintenance.}
        \jobSubItem{Designed a relational database using ER diagrams to structure and manage data.}
        \jobSubItem{Implemented CI/CD pipeline with automated testing and deployment, reducing development and integration time.}
        \jobSubItem{Created design documentation to ensure system maintainability and knowledge sharing.}
        \jobSubItem{Technologies used: Python, JavaScript, SQLite, Django, Bootstrap, GitLab, Bash.}
      \resumeItemListEnd

\jobSubheading
      {Thesis: Improving Programming Skills Training from Software Quality Perspective}{Jan. 2024 - Jul. 2024}
      {Overview: A research project focused on identifying the programming skills that can be developed through gameplay and proposing effective process to support programmers' skill training.}
      \resumeItemListStart
        \jobSubItem{Conducted data-driven analysis to identify key learning needs and proposed effective solution.}
        \jobSubItem{Automated data preprocessing to clean and structure raw data efficiently.}
        \jobSubItem{Reused existing tools and third-party libraries to optimize development efficiency.}
        \jobSubItem{Containerized required analysis tools via Docker images and integrated them into the data preprocessing pipeline.}
        \jobSubItem{\href{https://github.com/ptidejteam/ptidej-Ptidej/issues?q=is\%3Aissue\%20state\%3Aclosed\%20author\%3Ayihsuan1102}{Contributed to an open-source project} by identifying and reporting issues, enabling successful compilation and increasing build reliability for future researchers.}
        \jobSubItem{Technologies used: Python, JavaScript, SQLite, Docker, Oclint, PMD CPD, Github Copilot, Django, Gitlab.}
      \resumeItemListEnd
      \jobSubheading
  {Integrated Gesture Recognition System with Model Training}{Jul. 2019 - Jan. 2020}
  {Overview: A university capstone project that developed an automated vision testing system using pose estimation and gesture recognition to streamline the testing process.}
  \resumeItemListStart
    \jobSubItem{Designed and implemented an automated visual acuity testing system by integrating an existing pose estimation model with a self-trained LSTM-based gesture recognizer.}
    \jobSubItem{Processed joint coordinate sequences extracted from an existing gesture dataset and trained an LSTM model to classify motion patterns, achieving approximately 70\% accuracy.}
    \jobSubItem{Built a automated vision test interface using OpenCV for fixed-distance visual acuity testing with automated result processing.}
    \jobSubItem{Technologies used: Python, Bash, OpenCV, TensorFlow.}
  \resumeItemListEnd


\jobSubheading
      {\href{https://github.com/yihsuan1102/Service-management}{Lab Service Management Project}}{Aug. 2024}
      {Overview: A hands-on project designed to simulate real-world scenarios and practice deploying and managing services using container technologies.}
      
      \resumeItemListStart
        \jobSubItem{Simulated real-world service deployment by setting up GitLab, Nginx, and Mattermost in a Docker Compose environment with multi-host NFS storage.}
        \jobSubItem{Implemented container orchestration and monitoring with Portainer, gaining hands-on experience in scalable and maintainable infrastructure design.}
        \jobSubItem{Established a multi-host environment using NFS for shared storage, ensuring data consistency across nodes.}
        \jobSubItem{Technologies used: Linux, Docker, Nginx, Portainer, Gitlab.}
      \resumeItemListEnd

\jobSubheading
      {Data-driven Decision Making in Event Planning}{Nov. 2022- May 2024}
      {Overview: An in-lab event to encourage problem identification, brainstorming, and implementation among lab members.}
      \resumeItemListStart
        \jobSubItem{Organized an in-lab event with 12 participants to promote creative problem-solving and idea sharing, resulting in 3 most popular proposals developed over summer for future publication.}
        \jobSubItem{Transformed stakeholder needs into actionable event design that fostered creative discussion and collaborative project engagement.}
        \jobSubItem{Measured and analyzed event impact using questionnaire to drive continuous improvement.}
        \jobSubItem{Skills: Decision Making, Problem Solving, Communication, Project planning, Quality management.}
      \resumeItemListEnd

\jobSubheading
      {Leadership and Management during Proposal Writing}{Oct. 2022 - Dec. 2022}
      {Overview: A technical proposal submitted to the National Science and Technology Council (NSTC), aiming to improve delivery efficiency and user experience through smart logistics solutions.}
      
      \resumeItemListStart
        \jobSubItem{\textbf{Successfully passed} the proposal review and approval process.}
        \jobSubItem{Led a team of six members to submit the proposal on time while ensuring alignment with project goals.}
        \jobSubItem{Collaborated with the quality management team to ensure the proposal met required standards.}
        \jobSubItem{Planned the project schedule and monitored project progress by mentoring team members.}
        \jobSubItem{Skills: Team Collaboration, Communication, Documentation, Project management, Quality management.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Language}
      {Python, C/C++, Java, JavaScript, PHP, Bash}
      \resumeSubItem{Machine Learning}
      {TensorFlow, Pandas, Opencv, }
    \resumeSubItem{Web Development}
      {React, Django, HTML, CSS, Bootstrap,  Apache HTTP Server}
    \resumeSubItem{Database}
      {MySQL, Microsoft SQL Server, SQLite}
    \resumeSubItem{Software Engineering Capabilities}
      {Requirements engineering, Architectural design, Design and implementation, Software testing, Agile software development, Project management, Project planning, Quality management}
    \resumeSubItem{Tools}
      {Git, GitLab, Vim, Pycharm, YouTrack, SonarQube, Oclint, PMD CPD, Docker, Portainer, Nginx, VMvare, VitrualBox, ChatGPT, Claude, Github Copilot}
    \resumeSubItem{Operating System}
      {Windows, Linux}
    \resumeSubItem{Language}
      {Mandarin, English}
  \resumeSubHeadingListEnd

%-------------------------------------------

\end{document}
